### 2020-12-18 LaTeX-USENIX/sections/abstract.tex
eval frameworks edits

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancellation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').
\end{abstract}

>>>>

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancellation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market (or batch auction) exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').
\end{abstract}
